Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-03 conclusions.tex
reworked end
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@931 ccdd05d5-56c1-461a-bf98-85f6876523b4

We plan to explore more rigorously the prospects of early warning detection
with realistic simulations of binary mergers using the infrastructure and
techniques described here.  We will compare the performance of the early
warning pipeline sky localization capabilities with the theoretical
estimates~\cite{Fairhurst2009}.

\editorial{nvf: It's a bit pie-in-the-sky, but we could also mention reconfiguring
the signal recycling mirror to optimize SNR at merger. There's a lot of science there.}

>>>>

Although we have demonstrated a feasible method for advance detection we have
not explored the accuracy of sky localization that is possible before merger.
~\cite{Fairhurst2009} discusses some of the theoretical prospects for early sky
localization.  Our future work will explore the prospects of early warning
detection with realistic simulations of binary mergers using the infrastructure
and techniques described here.

\editorial{SHould we mention composite detection?}
\editorial{nvf: It's a bit pie-in-the-sky, but we could also mention reconfiguring
the signal recycling mirror to optimize SNR at merger. There's a lot of science there.}
